---
title: "hw001_Data frame exploration"
author: "Irissq28"
date: "16th September, 2018"
output: github_document
---

## Data frame exploration

### Setting up

First, check the existing packages in your computer. 
`data(package = .packages(all.available = TRUE))`

If you don't have the package you need, visit [Contributed Packages](https://cran.r-project.org), run `install.packages(yourpackage_name)` in the console first.

### Choose package and data set

Data set 'survey' in package ‘MASS’

'survey' is Student Survey Data

```{r}
library(MASS)
```

```{r}
print(survey)
```


### Exploration of data frames

Explore `survey` with functions like `head`, `tail`, `str`, `summary`.

```{r}
#print first 5 rows in survey
head(survey,n=5L)
#print last 2 rows in survey
tail(survey,n=2L)
#list the structure of survey
str(survey)
#result summaries
summary(survey)
```


### Exploratory plot of survey data frames

It summarizes the relationship between the 12 variables in 'survey' data frame
```{r}
plot(survey)
```

'smoke' versus 'height' from 'survey' data frame
```{r}
plot(survey$Smoke,survey$Height)
```
